Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-06-14 Manuscript/proto-manuscript.tex
Updates

Here we apply the same approach to lipid bilayers to accurately 
describe the lipid headgroup response to Na+ and Ca2+ concentrations \cite{catte16}. 
We use the Lipid14~\cite{dickson14} force field parameters as a starting point,
because they give the most realistic headgroup response with added cations 
and relatively realistic glycerol backbone and headgroup structures
when compared with other state of the art lipid models \cite{botan15,catte16}.
The partial atomic charges in Lipid14 were derived by fitting the electrostatic 
potential to its model quantum chemistry representation in vacuum.
\todo{SAMULI: I do not fully understand the end of this paragraph}
If such charges are obtained in an implicit solvent, 
they vary the most for the polar moieties \cite{maiejewski14}. 
In order to represent this difference in polarity in a model with fixed charges, 
we shall use the average charges from both environments (IpolQ charges) \cite{Cerutti2013}. 
By taking the charges of oxygen atoms in vacuum and implicit water solvent for POPC from \cite{maciejewski14}, 
we represent the IpolQ charges in the electronic continuum correction of the Lipid14 model
by increasing the scaling factor for charges to $f_q = 0.8$. 
\todo{SAMULI: I tried to repeat this calculation but I was not able to get 0.8.
This has to be explained better.}
The newly presented ECC-POPC model is based on the POPC model from

@@

The scaling of these partial charges by a factor of 0.8 reduce the 
area per molecule to ??, which is significantly smaller than the
experimental and original Lipid 14 values.  
The decrease of area was speculated 
\todo{Did you analyze the effect of this to hydration or did we only speculate?}
to arise from reduced hydration
of headgroup due to the lower polarity of molecules with scaled charges.
The hydration can be increased by decreasing the radius of atoms
by reducing $\sigma$ term in Lennart-Jones potential, which
allows water molecules approach closer to lipid atoms and
have stonger electrostatic interactions with them.
\todo{This effect may have an official name. In that case we should mention it.}
Indeed, the scaling of $\sigma$ increased the area per molecule
and the results close to experimental and original Lipid14 values were achieved
with scaling factor of ?? for $\sigma$ and 0.8 for partial charges.
%\todo{Is there some justification for the below sentence?} 
%In line with the electronic continnum correction,
%the scaling factor for sigma parameters, $f_\sigma$,
%has to lay between $f_q$ and 1.

@@

%\todo{ongoing,Actual concentration of cations in simulation has yet to be estimated. 
%If it varies too much from the nominal concentration, I may need to tweak the scaling 
%factors, $f_q$ or only $f_\sigma$, to accomodate it. However, it is very unlikely, response 
%to the surfactant \ce{DHMDMAB} is OK. Big patches with loads of solvent are running at the 
%moment to guide me on the possible finite-size errors and this conc-error.
The used experimental data reports order parameters as a function of
equilibrium cation concentration in bulk solvent \cite{akutsu81,altenbach84}.
The box size in simulations was adjusted such that ion conceration reaches 
a clear bulk plateau, which then gives the concentration that corresponds to the
one reported in experiments. The concentrations in units of mol/l were then 
determined as
\begin{equation}
  C_{eq}=\frac{C_{plateau}}{0.602},
\end{equation}
where plateau concentration is the number density in unist of 1/(nm)$^3$.

@@

@@

\subsection{Lipid bilayers without ions}
The scattering form factors, NMR order parameters and area per lipids calculated from 
the ECC corrected lipid model for POPC are compared to experiments and original
Lipid14 results in Fig. \ref{simVSexpNOions} and in Table~\ref{tab:apls}. 
%The optimal value for $f_\sigma$ was found by representing the overall membrane structure well
%by matching scattering form factors to experimental data~\cite{Petrache06, Kucerka08, Pabst10}.
The structural quality is comparable to the state of art lipid models available in literature \cite{ollila16},
thus we conclude that the ECC corrected lipid model reproduces the lipid bilayer structure
in liquid disordered phase with similar accuracy than other available models
\todo{Discussion to be finished when we have all the results in the figure}.
\begin{figure}[]
  \centering
  \includegraphics[height=8.5cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
%  \caption{\label{fig:form-f}
%    X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 and ECCLipids17 models.  }
%\end{figure}
%
%\begin{figure}[]
%  \centering
  \includegraphics[width=9.0cm]{../Fig/ipython_nb/Headgr_OPs_exp-L14-ECCL17.png}
  \caption{\label{simVSexpNOions}
    X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 and ECCLipids17 models. 
    Headgroup and glycerol backbone order parameters from simulations with Lipid14 \cite{dickson14} and EECLipid17 models
    compared with experimental order parameters from \cite{ferreira13}.}
  \todo{Add acyl chain order parameters, POPC chemical structure}
  \todo{Should we add the results from original lipid14?}
\end{figure}
%Area per molecules extracted from MD simulations and SPD model fitted to scattering data \todo{check that this the case for the used values}
%are shown in Table \ref{tab:apls}.
\todo{finalize figure (NMR headgr. OPs + SAXS, continue in the discussion.}
\begin{table}
  \caption{Area per lipid from different models for POPC without ions\label{tab:apls} }
  \begin{tabular}{c c c}
    model          & A (Å$^2$)   & Temperature [K] \\
    \hline
    Lipid14 (literature)  & 65.6$\pm$ 0.5  &  303 \\
    Lipid14ecc0.80+sigma0.875 &        &  313    \\
    GMX small patch           & 64.9   &         \\
    GMX 4xbig patch           & 65.5   &         \\
    oMM small patch           & 63.65  &         \\
    oMM 4xbig patch           & 63.7   &         \\
    \hline
    experiment \cite{Jambeck2012}\todoii{REF}{put original references, not Slipids param. paper.}  & 62.7  &  293    \\
    experiment  & 64.3  &  303    \\
    experiment  & 67.3  &  323    \\
    experiment  & 68.1  &  333    \\
    experiment POPE  & 56.6 &  303    \\
    \hline
  \end{tabular}
\end{table}

Headgroup order parameter response to bound charge was evaluated against
experimental data measured with cationic surfactant
(dihexadecyldimethylammonium bromide, C$_{12}$Cl$_{16}$$^+$N2C$_1$Br$^-$) \cite{scherer89}.
The exact amount of bound charge in the membrane is known these systems, because
practically all cationic surfactant molecules are embedded in lipid bilayer due to
their amphiphilic nature. Thus, the headgroup order parameter changes as a function of
mole fraction of cationic surfactants in  Fig. \ref{OrderParameterCHANGESnewMODELS} gives
also the order parameter changes as a function of bound cations.
\todo{I think that we should make a separate figures for this one and ion concentrations.
  In the current figure it would be difficult to show this with a reasonable scale.
  Currently Lipid14 results are cut out, thus the scale should be increased.
  This would, however, make the changes with CaCl too small.
  The change of headgroup tilt could be incorporated in the same figure with order parameter
  response to cationic surfactant.
}
The headgroup order parameter response to bound cation concentration
is approximately linear up to $\sim$0.3 mole fraction in experiments \cite{scherer89}.
The linearity is also observed in simulations with original Lipid14 and with ECC correction.
%from experiments \cite{seelig87} and simulations with Lipid14 model and with ECC-lipids model 
%as a function of bound charge are shown in
Quantitative comparison, however, reveals that the response is overestimated in 
original Lipid14 for both segments, while the ECC corrected model gives a
good agreement for the change of $\alpha$ segment order parameter, but slightly
underestimates the $\beta$ segment order parameter change.
The overestimation of order parameter changes with original Lipid14 model 
suggests that the overestimated response with CaCl$_2$ concentration in \cite{catte16} 
can be partly explained by the high sensitivity of the headgroup order parameter response
to bound charge.

@@

Ion density profiles between different simulation models are compared in Fig. \ref{fig:cacl-dens}.
Density profiles from simulations with original Lipid14 and Dang ions \cite{smith94,chang1999,dang2006} 
show a pronounced peak in the position of the phosphate moieties of POPC. 
The use of a ECC-ion model~\cite{kohagen14,kohagen16} along with original Lipid14 does not significantly change it
\todo{If we show density profile for this, we should show also the order parameter changes}.
The new ECC-lipid model with scaled ions exhibits on the other hand smaller density in this region 
suggesting overall weaker binding of cations (Fig.~\ref{OrderParameterCHANGESnewMODELS}). 
This demonstrates that cation binding in zwitterionic phospholipid bilayer can be accurately
described with classical MD simulation model with effective included of electronic polarizability.

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm,angle=0]{../Fig/CAdensities.eps}
  \caption{\label{fig:cacl-dens}
    Density profiles of \ce{Ca^{2+}} and \ce{Cl^-} for Lipid14 model with Aquist parameters
    and with ECC ions and ECCLipids17 with ECC ions. }
  \todo{We should add the location of bilayer here somehow.
    In NMRlipids II the location of phosphate was shown with green vertical line.}
  \todo{I would add Aqvist data from NMRlipids II in here as well.}
\end{figure}

One possible example is to adress the discourse on the stoichiometry of \ce{Ca^{2+}} binding 
to POPC~\cite{altenbach84}.
In line with the early experimental finding~\cite{altenbach84}, we find that our data 
fit well a ternary complex model, which assumes 2 POPC molecules per 1 \ce{Ca^{2+}}. 
In contrast to this experiment, however, we possess also a complete atomistic detail of this phenomenon.
Hence we can support this empirical finding with a direct observation of transient complexes of \ce{Ca^{2+}} and POPC.
The simulation suggests that the stoichiometry 2~POPC:1~\ce{Ca^{2+}} is the most common complex. 
In addition, there also is a non-negligable probability of one \ce{Ca^{2+}} cross-bridging three POPC molecules. 
This cannot be observed in experiments without atomistic detail as it makes only a small perturabation to 
the binding isotherm that assumes 2~POPC per 1~\ce{Ca^{2+}}. 
\todo{Analyze stoichiometry for \ce{Na^+}, \ce{Ca^{2+}}, their interaction energies with the lipid membrane, 
etc, and finalize the discussion after these results.}

It is also suggested that the addition of \ce{NaCl} to the solution of \ce{CaCl_2} enhances the hedgroup 
order parameter response compared to the solution with only \ce{CaCl_2}. \cite{altenbach84}
\todo{Simulate this effect and discuss it further}

\todo{The difference between DPPC and POPC -- simulate and compare with experiment. }

\begin{figure}[]
  \centering
  \includegraphics[height=9.0cm,angle=-90]{../Fig/bound-CAs_conc-eccl17.eps}
  \caption{\label{fig:cacl-bind}
    Binding isotherm assuming stoichiometry of 2~POPC:1~\ce{Ca^{2+}} as used in \cite{Altenbach84} fits the simulation data nicely.}
\end{figure}

@@

\section{Conclusions}
We show that the Na+ and Ca2+ binding in phospholipid bilayers can
be accurately described with MD simulation models, where electronic
polarization is effectively included by using ECC correction.
This is a significant advantage to the other available lipid models,
which all overestimate specific cation binding affinities.  
The proposed model reproduces the lipid bilayer structural details
with similar accuracy as the other state of the art lipid models.
overestimated cation binding in classical molecular
dynamics simulations can be corrected 
We present models of POPC and DPPC lipids that for the first time exhibit accurate headgroup order parameter response to cation binding. 
The models are derived from Lipid14 model \cite{dickson14} by applying the electronic continuum correction. 
The models were optimized to represent correct membrane structure, 
and they were validated with the use of electrometer concept \cite{seelig87,Altenbach85,Altenbach84}. 
Compared to the phenomenological observations of calcium:POPC stoichiometry in the experimental work \cite{Altenbach84}, 
our simulations reveal the same stoichiometry of 2~POPC molecules per 1~calcium but through direct observation. 
This tells us on the subtle effects of calcium in phospholipid membranes 
possibly leading to a better understanding of their physical properties (elasticity etc.). 
\todo{Improve this concluding-discussion with actual insights.}

>>>>

Here we apply the same approach to lipid bilayers to accurately 
describe the lipid headgroup response to Na+ and Ca2+ concentrations \cite{catte16}. 
We use the Lipid14~\cite{dickson14} force field parameters as a starting point,
because they give the most realistic headgroup response with added cations 
and relatively realistic glycerol backbone and headgroup structures
when compared with other state of the art lipid models \cite{botan15,catte16}.
The partial atomic charges in Lipid14 were derived by fitting the electrostatic 
potential to its model quantum chemistry representation in vacuum.
\todo{SAMULI: I do not fully understand the end of this paragraph}
If such charges are obtained in an implicit solvent, 
they vary the most for the polar moieties \cite{maciejewski14}. 
In order to represent this difference in polarity in a model with fixed charges, 
we shall use the average charges from both environments (IpolQ charges) \cite{Cerutti2013}. 
By taking the charges of oxygen atoms in vacuum and implicit water solvent for POPC from \cite{maciejewski14}, 
we represent the IpolQ charges in the electronic continuum correction of the Lipid14 model
by increasing the scaling factor for charges to $f_q = 0.8$. 
\todo{SAMULI: I tried to repeat this calculation but I was not able to get 0.8.
This has to be explained better.}
The newly presented ECC-POPC model is based on the POPC model from

@@

The scaling of these partial charges by a factor of 0.8 reduce the 
area per molecule to ??, which is significantly smaller than the
experimental and original Lipid 14 values.  
The decrease of area was speculated 
\todo{SAMULI: Did you analyze the effect of this to hydration or did we only speculate?}
to arise from reduced hydration
of headgroup due to the lower polarity of molecules with scaled charges.
The hydration can be increased by decreasing the radius of atoms
by reducing $\sigma$ term in Lennart-Jones potential, which
allows water molecules approach closer to lipid atoms and
have stonger electrostatic interactions with them.
\todo{SAMULI: This effect may have an official name. In that case we should mention it.}
Indeed, the scaling of $\sigma$ increased the area per molecule
and the results close to experimental and original Lipid14 values were achieved
with scaling factor of ?? for $\sigma$ and 0.8 for partial charges.
%\todo{Is there some justification for the below sentence?} 
%In line with the electronic continnum correction,
%the scaling factor for sigma parameters, $f_\sigma$,
%has to lay between $f_q$ and 1.

@@

%\todo{ongoing,Actual concentration of cations in simulation has yet to be estimated. 
%If it varies too much from the nominal concentration, I may need to tweak the scaling 
%factors, $f_q$ or only $f_\sigma$, to accomodate it. However, it is very unlikely, response 
%to the surfactant \ce{DHMDMAB} is OK. Big patches with loads of solvent are running at the 
%moment to guide me on the possible finite-size errors and this conc-error.
The used experimental data reports order parameters as a function of
equilibrium cation concentration in bulk solvent \cite{akutsu81,altenbach84}.
The box size in simulations was adjusted such that ion conceration reaches 
a clear bulk plateau, which then gives the concentration that corresponds to the
one reported in experiments. The concentrations in units of mol/l were then 
determined as
\begin{equation}
  C_{eq}=\frac{C_{plateau}}{0.602},
\end{equation}
where plateau concentration is the number density in unist of 1/(nm)$^3$.
\todo{SAMULI: Once we have to final results, we can probably say that
  the repeat distance is not far from the experimentally measured distance \cite{pabst07,uhrikova08}
  }

@@

\subsubsection{Simulations with cationic surfactants}
Automated topoly builder \cite{malde11} was first used to create pdb structure of
dihexadecyldimethylammonium bromide, C$_{12}$Cl$_{16}$$^+$N2C$_1$Br$^-$, molecule.
The AmberTools \cite{amber} was then used to generate the Amber force field
parameters from the pdb file. These were converted to Gromacs format by using
acpype tool \cite{acpype}. The partial charges were then manually modified
to approximately correspond the corresponding segments in Lipid14 \cite{dickson14}.
The surfactants were randomly mized with lipids to form bilayer structures with
mole fractions 10\%, 20\%, 30\%, 42\% and 50\% of surfctant in POPC bilayer.
Simulation parameters and force field for POPC was already used and
described previously \cite{catte16} and were downloaded from \cite{lipid14POPC0mMNaClfiles}.
The systems were simulated 100-200~ns at 313K and the first 20~ns of the trajectories
were excluded from the analysis as an equilibration period.
The simulations were ran with Gromacs 5~\cite{abraham15}. 
Simulation trajectories and parameters are available at \cite{??} \todo{To be uploaded to Zenodo}.

@@

\subsection{Lipid bilayers without ions}
The scattering form factors, NMR order parameters and area per lipids calculated from 
the ECC corrected lipid model for POPC are compared to experiments and original
Lipid14 results in Fig. \ref{simVSexpNOions} and in Table~\ref{tab:apls}. 
%The optimal value for $f_\sigma$ was found by representing the overall membrane structure well
%by matching scattering form factors to experimental data~\cite{Petrache06, Kucerka08, Pabst10}.
The structural quality is comparable to the state of art lipid models available in literature \cite{ollila16},
thus we conclude that the ECC corrected lipid model reproduces the lipid bilayer structure
in liquid disordered phase with similar accuracy than other available models
\todo{Discussion to be finished when we have all the results in the figure}.
\begin{figure}[]
  \centering
  \includegraphics[height=8.5cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
%  \caption{\label{fig:form-f}
%    X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 and ECCLipids17 models.  }
%\end{figure}
%
%\begin{figure}[]
%  \centering
  \includegraphics[width=9.0cm]{../Fig/ipython_nb/Headgr_OPs_exp-L14-ECCL17.png}
  \caption{\label{simVSexpNOions}
    X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 and ECCLipids17 models. 
    Headgroup and glycerol backbone order parameters from simulations with Lipid14 \cite{dickson14} and EECLipid17 models
    compared with experimental order parameters from \cite{ferreira13}.}
  \todo{Add acyl chain order parameters, POPC chemical structure}
  \todo{Should we add the results from original lipid14?}
\end{figure}
%Area per molecules extracted from MD simulations and SPD model fitted to scattering data \todo{check that this the case for the used values}
%are shown in Table \ref{tab:apls}.
\todo{finalize figure (NMR headgr. OPs + SAXS, continue in the discussion.}
\begin{table}
  \caption{Area per lipid from different models for POPC without ions\label{tab:apls} }
  \begin{tabular}{c c c}
    model          & A (Å$^2$)   & Temperature [K] \\
    \hline
    Lipid14 (literature)  & 65.6$\pm$ 0.5  &  303 \\
    Lipid14ecc0.80+sigma0.875 &        &  313    \\
    GMX small patch           & 64.9   &         \\
    GMX 4xbig patch           & 65.5   &         \\
    oMM small patch           & 63.65  &         \\
    oMM 4xbig patch           & 63.7   &         \\
    \hline
    experiment \cite{jambeck12}\todoii{REF}{put original references, not Slipids param. paper.}  & 62.7  &  293    \\
    experiment  & 64.3  &  303    \\
    experiment  & 67.3  &  323    \\
    experiment  & 68.1  &  333    \\
    experiment POPE  & 56.6 &  303    \\
    \hline
  \end{tabular}
\end{table}

Headgroup order parameter response to bound charge was evaluated against
experimental data measured with cationic surfactant
(dihexadecyldimethylammonium bromide, C$_{12}$Cl$_{16}$$^+$N2C$_1$Br$^-$) \cite{scherer89}.
The exact amount of bound charge in the membrane is known these systems, because
practically all cationic surfactant molecules are embedded in lipid bilayer due to
their amphiphilic nature. Thus, the headgroup order parameter changes as a function of
mole fraction of cationic surfactants in  Fig. \ref{OrderParameterCHANGESnewMODELS} gives
also the order parameter changes as a function of bound cations.
\todo{SAMULI: I think that we should make a separate figures for this one and ion concentrations.
  In the current figure it would be difficult to show this with a reasonable scale.
  Currently Lipid14 results are cut out, thus the scale should be increased.
  This would, however, make the changes with CaCl too small.
  The change of headgroup tilt could be incorporated in the same figure with order parameter
  response to cationic surfactant.
}
The headgroup order parameter response to bound cation concentration
is approximately linear up to $\sim$0.3 mole fraction in experiments \cite{scherer89}.
The linearity is also observed in simulations with original Lipid14 and with ECC correction.
%from experiments \cite{seelig87} and simulations with Lipid14 model and with ECC-lipids model 
%as a function of bound charge are shown in
Quantitative comparison, however, reveals that the response is overestimated in 
original Lipid14 for both segments, while the ECC corrected model gives a
good agreement for the change of $\alpha$ segment order parameter, but slightly
underestimates the $\beta$ segment order parameter change.
The overestimation of order parameter changes with original Lipid14 model 
suggests that the overestimated response with CaCl$_2$ concentration in \cite{catte16} 
can be partly explained by the high sensitivity of the headgroup order parameter response
to bound charge.

@@

Ion density profiles between different simulation models are compared in Fig. \ref{fig:cacl-dens}.
Density profiles from simulations with original Lipid14 and Dang ions \cite{smith94,chang1999,dang2006} 
show a pronounced peak in the position of the phosphate moieties of POPC. 
The use of a ECC-ion model~\cite{kohagen14,kohagen16} along with original Lipid14 does not significantly change it
\todo{SAMULI: If we show density profile for this, we should show also the order parameter changes}.
The new ECC-lipid model with scaled ions exhibits on the other hand smaller density in this region 
suggesting overall weaker binding of cations (Fig.~\ref{OrderParameterCHANGESnewMODELS}). 
This demonstrates that cation binding in zwitterionic phospholipid bilayer can be accurately
described with classical MD simulation model with effective included of electronic polarizability.
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm,angle=0]{../Fig/CAdensities.eps}
  \caption{\label{fig:cacl-dens}
    Density profiles of \ce{Ca^{2+}} and \ce{Cl^-} for Lipid14 model with Aquist parameters
    and with ECC ions and ECCLipids17 with ECC ions. }
  \todo{SAMULI: We should add the location of bilayer here somehow.
    In NMRlipids II the location of phosphate was shown with green vertical line.}
  \todo{SAMULI: I would add Aqvist data from NMRlipids II in here as well.}
\end{figure}

Good agreement of ECC corrected model with experiments encourages us to analyse the
binding details from MD simulations. Direct analysis of contacts between ions and
lipids from simulations suggest that most common complex are ones with stoichiometry
of 2~POPC:1~\ce{Ca^{2+}}.
\todo{SAMULI: Details of this analysis have to be added.}
As shown in Fig. \ref{fig:cacl-bind} this is in agreement
with the ternary complex model suggested based on headgroup order parameter
experiments~\cite{altenbach84}.
\todo{SAMULI: The same authors have also literature, where they say that ternary complex may not
  be the only option. I will recheck and come back to this.}
%This cannot be observed in experiments without atomistic detail as it makes only a small perturabation to 
%the binding isotherm that assumes 2~POPC per 1~\ce{Ca^{2+}}. 
\todo{SAMULI: I would also analyze how much there is contact between ions and different
parts of the lipid (phosphase, carbonyl, etc.).}
In addition to the ternary complexes, there also is a non-negligable probability
of one \ce{Ca^{2+}} cross-bridging three POPC molecules
\todo{SAMULI: I think we should quantify this, i.e. how much there are these.
  Maybe also the other possible complexes? Maybe also the correlation betweem complexes
  and binding cites, if it is not too much work.}.

\todo{Finalize stoichiometry analysis for \ce{Na^+}, \ce{Ca^{2+}},
  their interaction energies with the lipid membrane, etc,
  and finalize the discussion after these results.}

%It is also suggested that the addition of \ce{NaCl} to the solution of \ce{CaCl_2} enhances the hedgroup 
%order parameter response compared to the solution with only \ce{CaCl_2}. \cite{altenbach84}
%\todo{Simulate this effect and discuss it further}

%\todo{The difference between DPPC and POPC -- simulate and compare with experiment. }

\begin{figure}[]
  \centering
  \includegraphics[height=9.0cm,angle=-90]{../Fig/bound-CAs_conc-eccl17.eps}
  \caption{\label{fig:cacl-bind}
    Binding isotherm assuming stoichiometry of 2~POPC:1~\ce{Ca^{2+}} as used in \cite{altenbach84} fits the simulation data nicely.}
\end{figure}

@@

\section{Conclusions}
We show that the Na+ and Ca2+ binding in phospholipid bilayers can
be accurately described with MD simulation models, where electronic
polarization is effectively included by using ECC correction.
This is a significant advantage to the other available lipid models,
which all overestimate specific cation binding affinities.  
The proposed model reproduces the lipid bilayer structural details
with similar accuracy as the other state of the art lipid models.
The correction is applied here on Lipid14 POPC model \cite{dickson14},
but we expect that the correction can be generalized also for other lipids
and force fields.
%The models were optimized to represent correct membrane structure, 
%and they were validated with the use of electrometer concept \cite{seelig87,Altenbach85,Altenbach84}.

Direct analysis of calcium binding details from MD simulations is in agreement
with ternary complex model, which is suggested based on NMR data \cite{altenbach84}.
In this model 1~calcium binds to 2~POPC molecules, which together form a ternary
complex.
%This tells us on the subtle effects of calcium in phospholipid membranes 
%possibly leading to a better understanding of their physical properties (elasticity etc.). 
%\todo{Improve this concluding-discussion with actual insights.}
